
# _**TESTY**_

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Obliczanie kwoty wydanej na kawę za pomocą wartości przypisanych do zmiennych
```{r}
# Zapisywanie 3 w zmiennej
num_cups_coffee <- 3
# Zapisywanie 3.5 w zmiennej coffee_price.
coffee_price <- 3.5
# Łączne wydatki na kawę.
money_spent_on_coffee <- num_cups_coffee * coffee_price 
print(money_spent_on_coffee)
```

Obliczanie liczby sekund w roku
```{r}
second_in_a_year <- 365 * 24 * 60 * 60
print(second_in_a_year)
```
**PRZYKŁAD TABELKI**

Table Header | Second Header
------------- | -------------
Table Cell | Cell 2
Cell 3 | Cell 4


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

```{r}
```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
